Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels

### 2019-04-09 ICPP-19/communications.tex
Adjusting plots

		As \textit{Transfer time = Latency + (Data Volume)/Bandwidth}. For simplicity, we consider input transfer time is same as input data volume (i.e., \textit{Latency=0} and \textit{Bandwidth=1}). Otherwise, we can adjust $C$ such that at any point in a schedule at max one $K_i$ and three $A_i$ tasks can be active.

@@

		Figures ~\ref{fig:ratio_to_optimal_hf} and ~\ref{fig:ratio_to_optimal_ccsd} depict the distribution of the performance of each heuristic for all considered memory capacities, where plots are categorized by memory capacities. For each memory capacity and each heuristic, the box on the plot displays the median, first and last quartile, and the whiskers indicate minimum and maximum values, with outliers are shown by black dots.
		\subsection{HF Performance}	
		%%	\begin{figure*}[htb]
		%%		\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_selected_hf.pdf}
		%%		\caption{Comparison of different heuristics for HF.}
		%%		\label{fig:ratio_to_optimal_hf}
		%%	\end{figure*}
		\begin{figure*}[htb]
			\includegraphics[scale=0.25]{./all-binpack/ratio_to_optimal_selected_hf.pdf}
			\caption{Comparison of different heuristics for HF.}
			\label{fig:ratio_to_optimal_hf}
		\end{figure*}
		As indicated above, HF tasks are highly homogeneous, this is also noticeable in Figure~\ref{fig:ratio_to_optimal_hf}. All heuristics depict similar behavior for minimum memory capacity $m_c$ and increasing the memory capacity slightly does not change the performance of all heuristics. As memory capacity increased further, dynamic variants of heuristics starts performing better and for the moderate memory capacities (close to $2m_c$ ), static order with dynamic correction variants outperform others. $GG$ heuristic does not achieve good performance. It can be explained from the fact that the task sequence is obtained considering no extra memory is available, but here we apply the same sequence for a different scenario, overall memory consumed at each point is limited to memory capacity. $BP$ heuristic does not take the advantage of task types, hence it performs poorly in most cases.

		\begin{figure}[htb]
			\includegraphics[scale=0.15]{./results/plots/inverse_ratio_to_optimal_hf-best.pdf}
			\caption{Comparision of best variants of all categories for HF.}
			\label{fig:ratio_to_optimal_best_hf}
		\end{figure}

@@

		\begin{figure*}[htb]
			\includegraphics[scale=0.25]{./all-binpack/ratio_to_optimal_selected_ccsd.pdf}
			\caption{Comparison of different heuristics for CCSD.}
			\label{fig:ratio_to_optimal_ccsd}
		\end{figure*}

@@

		\begin{figure}[htb]
			\includegraphics[scale=0.15]{./results/plots/inverse_ratio_to_optimal_ccsd-best.pdf}
			\caption{Comparision of best variants of all categories for CCSD.}
			\label{fig:ratio_to_optimal_best_ccsd}
		\end{figure}

@@

		\begin{figure}[htb]
			%\begin{tabular}{c}
			\subfloat[HF workloads\label{fig:hfProperties}]{%
				\includegraphics[width=.45\linewidth]{./results/plots/application_properties_hf.pdf}
			}%\\
			\subfloat[CCSD workloads\label{fig:ccsdProperties}]{%
				\includegraphics[width=.45\linewidth]{./results/plots/application_properties_ccsd.pdf}
			}%\\
			%\end{tabular}
			\caption{HF and CCSD tasks characteristics.}
			\label{fig:ApplicationProperties}
		\end{figure}

@@

		\begin{figure*}[htb]
			\subfloat[Best variants of HF.\label{fig:hf_best_variants_batch}]{%
				\includegraphics[width=.45\linewidth]{./results/plots/inverse_ratio_to_optimal_hf_batch-best.pdf}
			}%\\
			\subfloat[Best variants of CCSD.\label{fig:ccsd_best_variants_batch}]{%
				\includegraphics[width=.45\linewidth]{./results/plots/inverse_ratio_to_optimal_ccsd_batch-best.pdf}
			}%\\
			\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
			\label{fig:best_variants_batch}
		\end{figure*}

>>>>

		As \textit{Transfer time = Latency + (Data Volume)/Bandwidth}. For simplicity, we consider input transfer time is same as input data volume (i.e., \textit{Latency = 0} and \textit{Bandwidth = 1}). Otherwise, we can adjust $C$ such that at any point in a schedule at max one $K_i$ and three $A_i$ tasks can be active.

@@

		Figures ~\ref{fig:ratio_to_optimal_hf} and ~\ref{fig:ratio_to_optimal_ccsd} depict the distribution of the performance of each heuristic for all considered memory capacities, where plots are categorized by memory capacities. For each memory capacity and each heuristic, the box on the plot displays the median, first and last quartile, and the whiskers indicate minimum and maximum values, with outliers are shown by black dots.
		\subsection{HF Performance}	
		%%	\begin{figure*}[htb]
		%%		\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_selected_hf.pdf}
		%%		\caption{Comparison of different heuristics for HF.}
		%%		\label{fig:ratio_to_optimal_hf}
		%%	\end{figure*}
		\begin{figure*}[htb]
		  \includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_hf.pdf}
			\caption{Comparison of different heuristics for HF.}
			\label{fig:ratio_to_optimal_hf}
		\end{figure*}
		As indicated above, HF tasks are highly homogeneous, this is also noticeable in Figure~\ref{fig:ratio_to_optimal_hf}. All heuristics depict similar behavior for minimum memory capacity $m_c$ and increasing the memory capacity slightly does not change the performance of all heuristics. As memory capacity increased further, dynamic variants of heuristics starts performing better and for the moderate memory capacities (close to $2m_c$ ), static order with dynamic correction variants outperform others. $GG$ heuristic does not achieve good performance. It can be explained from the fact that the task sequence is obtained considering no extra memory is available, but here we apply the same sequence for a different scenario, overall memory consumed at each point is limited to memory capacity. $BP$ heuristic does not take the advantage of task types, hence it performs poorly in most cases.

		\begin{figure}[htb]
			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_hf-best.pdf}
			\caption{Comparision of best variants of all categories for HF.}
			\label{fig:ratio_to_optimal_best_hf}
		\end{figure}

@@

		\begin{figure*}[htb]
			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_ccsd.pdf}
			\caption{Comparison of different heuristics for CCSD.}
			\label{fig:ratio_to_optimal_ccsd}
		\end{figure*}

@@

		\begin{figure}[htb]
			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_ccsd-best.pdf}
			\caption{Comparision of best variants of all categories for CCSD.}
			\label{fig:ratio_to_optimal_best_ccsd}
		\end{figure}

@@

%%		\begin{figure}[htb]
%%			%\begin{tabular}{c}
%%			\subfloat[HF workloads\label{fig:hfProperties}]{%
%%				\includegraphics[width=.45\linewidth]{./results/plots/application_properties_hf.pdf}
%%			}%\\
%%			\subfloat[CCSD workloads\label{fig:ccsdProperties}]{%
%%				\includegraphics[width=.45\linewidth]{./results/plots/application_properties_ccsd.pdf}
%%			}%\\
%%			%\end{tabular}
%%			\caption{HF and CCSD tasks characteristics.}
%%			\label{fig:ApplicationProperties}
%%		\end{figure}

		\begin{figure}[htb]
	%\begin{tabular}{c}
		\includegraphics[scale=0.5]{./results/plots/application_properties.pdf}
	\caption{HF and CCSD tasks characteristics.}
	\label{fig:ApplicationProperties}
	\end{figure}

@@

%%		
%%		\begin{figure*}[htb]
%%			\subfloat[Best variants of HF.\label{fig:hf_best_variants_batch}]{%
%%				\includegraphics[width=.45\linewidth]{./results/plots/inverse_ratio_to_optimal_hf_batch-best.pdf}
%%			}%\\
%%			\subfloat[Best variants of CCSD.\label{fig:ccsd_best_variants_batch}]{%
%%				\includegraphics[width=.45\linewidth]{./results/plots/inverse_ratio_to_optimal_ccsd_batch-best.pdf}
%%			}%\\
%%			\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
%%			\label{fig:best_variants_batch}
%%		\end{figure*}

\begin{figure*}[htb]
		\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_batch-best.pdf}
	\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
	\label{fig:best_variants_batch}
\end{figure*}
